Backpropagating Gravitational wave events

### 2022-03-29 src/ms.tex
WIP: edits to Methods Section

Once all the parameters including a particular draw of all the random variables are known,
the population synthesis code is a deterministic function that transforms the properties of the progenitors into the GW parameters.
Hence, the probability of obtaining a GW event with parameters $\bm{\theta}$ given the progenitor parameters $\bm{\theta}'$ is given by

@@

where $\bm{f}$ represents the population synthesis code.

>>>>

Once all the parameters including a particular draw of all the random variables are known,
the population synthesis code is a deterministic function that transforms the properties of the progenitors into the GW parameters.
Hence, the probability of obtaining a GW event with parameters $\bm{\theta}$ given the progenitor parameters $\bm{\Theta}$ is given by

@@

where $\bm{f}$ represents the evolution encoded by the population synthesis model with fixed random parameters $\bm{X}$.
